---
title: "Dataset Descriptives"
format: html
editor: visual
---

## Loading Libraries

```{r}
library(pacman)
p_load(tidyverse, janitor)
```

## Loading the Data

```{r}
data <- read_csv(
  "data.csv",
  show_col_types = F
) %>%
  clean_names()

glimpse(data)
```

## Dataset Descriptives Original

```{r}
data
```


## Dataset Descriptives Replication

Original statement:

> Since the frequency and duration of greenspace use were highly correlated (`r(2,998) = 0.696, P \< 0.0001`)

```{r}
cor.test(
  data$greenspace_use_frequency,
  data$greenspace_use_duration,
  method = "pearson"
)
```


Original statement:

> Our sample participants represented the full range of different age groups.

```{r}
summary(data$age)
```

```{r}
#| echo: false
data %>%
  ggplot(aes(age)) +
  geom_histogram(binwidth = 5, fill = "#177e89", color = "white") +
  labs(x = "Age", y = "Count (participants)") +
  theme_linedraw() +
  theme(panel.grid = element_blank())
```


Original statement:

> The number of male and female participants was the same (1,500 of each)

```{r}
table(data$sex)
```


Original statement:

> Among the 3,000 participants, there was marked variation in the five mental health outcomes (Fig. 1)

```{r}
behav_vars <- c("depression_and_anxiety", "life_satisfaction", "self_esteem", "subjective_happiness", "loneliness")

data %>%
  mutate(across(all_of(behav_vars), scale)) %>%
  pivot_longer(cols = all_of(behav_vars)) %>%
  ggplot(aes(value)) +
  geom_density(color = "#177e89") +
  facet_grid(rows = "name") +
  labs(x = "Z-Scored Value", y = "Density") +
  theme_linedraw() +
  theme(panel.grid = element_blank())
```


Original statement:

> The frequency of greenspace use varied widely across participants, but the majority of participants did not visit any greenspace in May 2020

```{r}
data %>%
  pivot_longer(cols = c(greenspace_use_frequency, greenspace_use_duration)) %>%
  ggplot(aes(value)) +
  geom_histogram(bins = 10, fill = "#177e89", color = "white") +
  facet_wrap(~name, scales = "free_x") +
  labs(x = "Value (see paper)", y = "Count (participants)") +
  theme_linedraw() +
  theme(panel.grid = element_blank())
```

Original statement:

> Approximately 81% of the participants reported that their home had a view of nature

```{r}
prop.table(table(data$nature_view))
```

